Analyzing Toronto's Dining Scene: Public Food Safety and Economic Indicators in Focus

### 2024-01-23 Outputs Folder/paper_final.qmd
Update paper_final.qmd

@@

cpi_data <- read_csv("/cloud/project/Inputs Folder/Data/Clean_CPI_Data.csv") %>%
  filter(measure_name == "CPI - Consumer Price Index - Toronto (% Change)") %>%
  rename(CPI = measure_value) %>%
  mutate(Year = as.numeric(year)) %>%
  group_by(Year) %>%
  summarize(Average_CPI = mean(CPI, na.rm = TRUE))

dataset <- read_csv("/cloud/project/Inputs Folder/Data/Clean_Dinesafe_Data.csv") %>%
  mutate(Inspection_Date = as.Date(`Inspection Date`, format = "%Y-%m-%d")) %>%
  mutate(Year = as.numeric(format(Inspection_Date, "%Y"))) %>%
  group_by(Year) %>%
  summarize(Total_Infractions = n())

@@

file_path <- "/cloud/project/Inputs Folder/Data/Clean_Dinesafe_Data.csv"
dataset <- read_csv(file_path)

@@

file_path <- "/cloud/project/Inputs Folder/Data/Clean_CPI_Data.csv"

>>>>

dataset <- read_csv("Inputs Folder/Data/Clean_Dinesafe_Data.csv")

@@

cpi_data <- read_csv("Inputs Folder/Data/Clean_CPI_Data.csv") %>%
  filter(measure_name == "CPI - Consumer Price Index - Toronto (% Change)") %>%
  rename(CPI = measure_value) %>%
  mutate(Year = as.numeric(year)) %>%
  group_by(Year) %>%
  summarize(Average_CPI = mean(CPI, na.rm = TRUE))

dataset <- read_csv("Inputs Folder/Data/Clean_Dinesafe_Data.csv") %>%
  mutate(Inspection_Date = as.Date(`Inspection Date`, format = "%Y-%m-%d")) %>%
  mutate(Year = as.numeric(format(Inspection_Date, "%Y"))) %>%
  group_by(Year) %>%
  summarize(Total_Infractions = n())

@@

file_path <- "Inputs Folder/Data/Clean_Dinesafe_Data.csv"
dataset <- read_csv(file_path)

@@

file_path <- "Inputs Folder/Data/Clean_CPI_Data.csv"
